rbeast2: BEAUti 2, BEAST2 and Tracer for R

### 2018-02-19 article.tex
Add what rbeast2 cannot do

>>>>

Currently, \verb;rbeast2; does not replace all functionality in BEAUti,
as it does not supply 3 out of 7 tree priors, nor does it support RNA
alignments or use of morphological data. The many plug-ins of BEAUti
are not supported by \verb;rbeast2;. \verb;rbeast2; does not support
all command-line arguments of BEAST2, does not supply
the more specialized Tracer analysis options, nor is it as feature-rich
in plotting options as DensiTree. Up until now, the \verb;rbeast2; features 
implemented are those requested by users. Further extension of \verb;rbeast2; 
will have to come from future user requests.
